Grove: A Convergent Collaborative Structure-Editor Calculus

### 2020-07-03 grove-paper.tex
Trying to get preview working in Overleaf
Make files be editable in Overleaf

\begin{figure}
\centering 
\includegraphics{simpletreewithholeX.dot}
%\digraph[]{simpletreewithholeX}{
%  node [shape=Mrecord,fontsize=11,ranksep=0];
%  edge [arrowhead=vee,fontsize=11,weight=2];
%  rankdir = LR;
%  {rank=min; n0 [shape=point]};
%  n0 [label="{0: Root_root|{<root> root}}",style=filled,fillcolor=black];
%  n3 [label="{3: Exp_plus|{<left> left|<right> right}}",style=filled,fillcolor=white];
%  n6 [label="{6: Exp_num(2)|{}}",style=filled,fillcolor="#ddffdd"];
%  n3:left -> n6 [color=black,label="7",edgeURL="#"];
%  n0:root -> n3 [color=black,label="4",edgeURL="#"]}
\begin{tikzpicture}
% TODO: texttt
% TODO: position the different graphs
\path (0cm,0cm) graph[tree layout] {
  + -> {
    2[as={\texttt{2}}],
    % <empty>
  }
};
\end{tikzpicture}
\caption{Scenario X: Holes in the Tree}
\label{fig:Scenario X: Holes in the Tree}
\end{figure}

@@

\begin{figure}
\centering
\begin{tikzpicture}
% TODO: texttt
% TODO: position the different graphs
\path (0cm,0cm) graph[tree layout] {
  + -> {
    3[as={\texttt{3}}], % TODO: put a cursor (green) here
    4 % TODO: put a cursor (red) here
  }
};
\path (-3cm,-2cm) graph[tree layout] {
  + -> {
    13, % TODO: put a cursor here
    4
  }
};
\path (3cm,-2cm) graph[tree layout] {
  + -> {
    3,
    14 % TODO: put a cursor here
  }
};
\path (0cm,-4cm) graph[tree layout] {
  + -> {
    13, % TODO: put a cursor here
    14 % TODO: put a cursor here
  }
};
\end{tikzpicture}
\caption{Scenario A: Editing Different Parts of the Code}
\label{fig:Scenario A: Editing Different Parts of the Code}
\end{figure}

>>>>

\begin{figure}
\centering 
\includegraphics[scale=0.75]{graphviz/simple-tree-with-hole.dot}
\caption{Scenario X: Holes in the Tree}
\label{fig:Scenario X: Holes in the Tree}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale=0.75]{graphviz/editing-different-parts-of-the-code-1.dot}
\includegraphics[scale=0.75]{graphviz/editing-different-parts-of-the-code-2.dot}
\includegraphics[scale=0.75]{graphviz/editing-different-parts-of-the-code-3.dot}
\includegraphics[scale=0.75]{graphviz/editing-different-parts-of-the-code-4.dot}
\caption{Scenario A: Editing Different Parts of the Code}
\label{fig:Scenario A: Editing Different Parts of the Code}
\end{figure}
